Outline

### 2021-10-06 text/suppl_tables_figures.Rmd
:fish:

loadd(SI_fig1)
loadd(SI_fig2)
loadd(SI_pp_plots)
loadd(SI_rank_plots)
```

@@

  flextable(data) %>%
    fontsize(size = 8) %>%
    fontsize(size = 10, part = "header") %>%
    set_caption("Extended Date table 2: Overview of localities of UVC transects, used in this study, including number of sites and number of transects") %>%
    autofit()
```

```{r, echo = FALSE}
  tab <- tidy(readd(mod_mvfun_com))
test <- summary(tab)$summary %>% 
  as.data.frame() %>%
  tibble::rownames_to_column("name") %>%
  tidyr::separate(name, into = c("dep", "var", "extra"), sep = "_") %>%
  dplyr::mutate(var = paste0(var, extra)) %>%
  table <- 
    tidy(tab) %>%
    mutate_if(is.numeric, round, 4) %>%
    mutate(term = c("intercept",
                    "sst",
                    "log(biomass)",
                    "richness",
                    "size (mean)", "trophic level (mean)", "immaturity (mean)",
                    "size (97.5)", "trophic level (97.5%)", "immaturity (2.5%)",
                    "immaturity (97.5%)", "trophic level (2.5%)", "size (2.5%)"
                    )) %>%
    mutate(response = "log(N excretion)")
  flextable(table) %>%
    fontsize(size = 8) %>%
    fontsize(size = 10, part = "header") %>%
    merge_v(j = 1) %>% 
    border_inner_h(border = fp_border(color = "black", style = "solid", width = 1)) %>%
    set_caption("Extended Date table 2: Overview of parameters of the regressions relating the five functions to the community structure variables") %>%
    autofit()
```

@@

![Extended Data Figure 1: a-e) Relationship between biomass and the five functions. Lines and shaded areas show the average and 95% credible interval of the predicted functions respectively, for a constant sea surface temperature of 26°C (the average across all sites). Vertical lines show the range of the estimated functions across fish communities per biomass class of 100g/m2. f) Fold variation of each function per biomass class of 100g/m2 across fish communities. g) Correlation matrix of the residuals of the five functions after regression with biomass and sea surface temperature. Standard deviations of correlation coefficients did not exceed 0.01.](../output/plots/annex_fig1.png)

>>>>

# loadd(SI_fig1)
# loadd(SI_fig2)
# loadd(SI_pp_plots)
# loadd(SI_rank_plots)
```

@@

  flextable(data) %>%
    fontsize(size = 8) %>%
    fontsize(size = 10, part = "header") %>%
    set_caption("Extended Date table 1: Overview of localities of UVC transects, used in this study, including number of sites and number of transects") %>%
    autofit()
```

```{r, echo = FALSE}
 table <- readd(tab_mod_mv_siteloc)
  flextable(table) %>%
    fontsize(size = 8) %>%
    fontsize(size = 10, part = "header") %>%
    merge_v(j = 1) %>% 
    border_inner_h(border = fp_border(color = "black", style = "solid", width = 1)) %>%
    set_caption("Supplementary table 2: Overview of parameters of the multivariate regression predicting the five functions with intercepts only.") %>%
    autofit()
```

```{r, echo = FALSE}
 table <- readd(tab_mod_mvfun_bm)
  flextable(table) %>%
    fontsize(size = 8) %>%
    fontsize(size = 10, part = "header") %>%
    merge_v(j = 1) %>% 
    border_inner_h(border = fp_border(color = "black", style = "solid", width = 1)) %>%
    set_caption("Supplementary table 3: Overview of parameters of the multivariate regression predicting the five functions with biomass and sst.") %>%
    autofit()
```

```{r, echo = FALSE}
 table <- readd(tab_mod_mvfun_com)
  flextable(table) %>%
    fontsize(size = 8) %>%
    fontsize(size = 10, part = "header") %>%
    merge_v(j = 1) %>% 
    border_inner_h(border = fp_border(color = "black", style = "solid", width = 1)) %>%
    set_caption("Supplementary table 4: Overview of parameters of the multivariate regression predicting the five functions and community variables.") %>%
    autofit()
```

@@

![Extended Data Figure 1: Correlations among functions, independent of biomass and sst, on the locality and site level.](../output/plots/figSx_corplot.png)
